%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Resume Template
% Version 2.0 (pdflatex compatible)
%
% This template is robust and designed to compile with standard LaTeX editors.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt, letterpaper]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}

% --- FONT CONFIGURATION ---
% Use Helvetica as the primary font
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% --- PAGE LAYOUT ---
\geometry{
    a4paper,
    left=0.75in,
    right=0.75in,
    top=0.5in,
    bottom=0.5in,
    footskip=.25in
}

% --- CUSTOMIZATION ---
% Define hyperlink colors (subtle blue)
\definecolor{linkcolor}{HTML}{0056b3}
\hypersetup{
    colorlinks=true,
    urlcolor=linkcolor,
    linkcolor=linkcolor
}

% Remove page numbers
\pagestyle{empty}

% Define section formatting (line below section title)
\titleformat{\section}
    {\bfseries\large\scshape\raggedright}
    {}
    {0em}
    {}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% Define custom list environment for experience/projects
\setlist[itemize]{
    leftmargin=*,
    label=\textbullet,
    noitemsep,
    topsep=0pt,
    partopsep=0pt
}

% Custom command for subheadings (e.g., job titles)
\newcommand{\resumeSubheading}[3]{%
    \item
    \begin{tabularx}{\textwidth}{@{}l X r@{}}
        \textbf{#1} & \textit{\small #2} & \textit{\small #3}
    \end{tabularx}%
}

% --- DOCUMENT START ---
\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge\bfseries\scshape Rounak Das}
    \vspace{3pt}
    
    \small
    \faMapMarker* Prayagraj, Uttar Pradesh \quad
    \faPhone\ +91 87774 73417 \quad
    \href{mailto:rounakdas2025@gmail.com}{\faEnvelope\ rounakdas2025@gmail.com} \\[3pt]
    \href{https://az9tumas.github.io/my-portfolio/}{\faGlobe\ az9tumas.github.io/my-portfolio} \quad
    \href{https://linkedin.com/in/rounak-das-600a99315}{\faLinkedin\ linkedin.com/in/rounak-das-600a99315} \quad
    \href{https://github.com/az9tumas}{\faGithub\ github.com/az9tumas}
\end{center}
\vspace{-2pt}

% --- SUMMARY ---
\section*{Summary}
Computer Science undergraduate with strong project-based experience in AI-driven applications, game development, and system/software architecture. Built machine learning prototypes, gameplay systems, and full-stack tools using Python, C++ and Lua, with emphasis on performance, debugging, and maintainable code. Currently seeking internships where I can deepen my work on AI and high-performance software systems.

% --- TECHNICAL SKILLS ---
\section*{Technical Skills}
\begin{tabularx}{\textwidth}{@{}l X}
    \textbf{Languages} & Python, C/C++, Lua, JavaScript/TypeScript, Java, SQL \\
    \textbf{Frameworks \& Libraries} & React.js, Node.js, ShadCN, NumPy, Pandas, Scikit-learn, Firebase, SDL \\
    \textbf{Developer Tools} & Git/GitHub, Neovim, Roblox Studio, Docker, Linux Terminal, CI/CD (GitHub Actions) \\
    \textbf{Platforms \& OS} & Windows, Linux, MacOS \\
    \textbf{Core Competencies} & Data Structures and Algorithms (DSA), Object-Oriented Programming (OOPs), System Design, Compiler Design, Network Configuration \& Troubleshooting \\
\end{tabularx}

% --- PROFESSIONAL EXPERIENCE ---
\section*{Professional Experience}
\begin{itemize}
    \resumeSubheading
        {Freelance Game Developer}
        {Roblox Platform}
        {May 2021 -- Present}
    \begin{itemize}
        \item Architected and engineered systems for 15+ game titles, leading development from concept to deployment in collaboration with artists and designers.
        \item Implemented robust, scalable datastore systems ensuring data integrity and persistence for thousands of concurrent users.
        \item Developed modular combat frameworks and custom physics for movement and vehicle mechanics (air/water), enhancing gameplay and user engagement.
        \item Engineered complex NPC AI using pathfinding (A*) and finite state machines, creating dynamic and responsive game environments.
    \end{itemize}
\end{itemize}

% --- PERSONAL PROJECTS ---
\section*{Personal Projects}
\begin{itemize}
    \resumeSubheading
        {Bytecode Programming Language}
        {C++, Compiler Design}
        {2022}
    \begin{itemize}
        \item Designed and built a custom bytecode-interpreted programming language from scratch, featuring a compiler and a virtual machine for execution.
        \item Implemented support for core language features, including global/local variables, function calls, and control flow structures.
    \end{itemize}

    \resumeSubheading
        {Game Boy Color Emulator}
        {C/C++, System Architecture}
        {Ongoing}
    \begin{itemize}
        \item Developed a functional CPU emulator for the Game Boy Color, focusing on instruction set accuracy and performance optimization.
        \item Successfully passed standard CPU validation tests, demonstrating a deep understanding of low-level system architecture.
    \end{itemize}

    \resumeSubheading
        {Full-Stack Web Applications}
        {React.js, Node.js, Web Frameworks}
        {Oct 2024 -- Present}
    \begin{itemize}
        \item Participated in college hackathons to build full-stack applications, including a collaborative study app and a real-time attendance tracker.
        \item Explored and implemented both front-end and back-end frameworks to deliver complete web solutions.
    \end{itemize}
    
     \resumeSubheading
        {Open Source Contributions}
        {Embedded Systems, Python}
        {Ongoing}
    \begin{itemize}
        \item Contributed to the PocketPy project, an embedded programming ecosystem, by submitting bug fixes and feature enhancements.
    \end{itemize}
\end{itemize}

% --- EDUCATION ---
\section*{Education}
\begin{itemize}
    \resumeSubheading
        {Motilal Nehru National Institute of Technology (MNNIT)}
        {Prayagraj, India}
        {Expected May 2028}
    \item[] \textit{Bachelor of Technology in Computer Science \& Engineering}
    
    \resumeSubheading
        {Indian School Muscat}
        {Muscat, Oman}
        {Graduated Apr 2024}
    \item[] \textit{Higher Secondary Examination (CBSE) -- Scored 95.4\%}
\end{itemize}

% --- ACHIEVEMENTS & AWARDS ---
\section*{Achievements \& Awards}
\begin{itemize}[label={}]
    \item \textbf{Chairman's Award (2024):} Awarded for achieving the highest grade (A1) in all subjects in the national CBSE board examinations.
    \item \textbf{Principal's Award for Academic Excellence (2024):} Recognized for outstanding overall scholastic performance in Class 12.
\end{itemize}

\end{document}
